---
title       : Interactive Regression Model
subtitle    : Slidify presentation for Developing Data Products
author      : Cutberto Paredes
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
ext_widgets : {rCharts: [libraries/nvd3]}
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = FALSE)
knitr::opts_chunk$set(message =  FALSE)
```
## Introduction

- This shiny app let's the user build a regression model for mpg usin the mtcars
dataset.

- You only have to select which regressors you wanna use and the app will return
the coefficients, $r^2$ values and a standardized residuals QQ plot.

---
## Pairs plot

This plot may help you select regressors.

```{r ggpairs, echo = FALSE, fig.width=12, fig.align='center'}
library(ggplot2)
library(GGally)
ggpairs(mtcars, mapping = aes(bins = 25))
```

---
## The app itself

- The app is included below as an iframe, but it's also available here: https://cparedes.shinyapps.io/shiny/

- This is how it looks:

<center><img src=figure/shinny.jpg></center>

---
## Interactive Plot

This rCharts plot shows the relationship between $mpg$ and $hp$, a regressor I 
suggest to include.

```{r plot, echo = FALSE, results = 'asis'}
library(rCharts)
library(knitr)
mtcars$am <- factor(mtcars$am, labels = c('Automatic', 'Manual'))
n1 <- rPlot(mpg ~ hp, data = mtcars, color = 'am', type = 'point')
n1
```