---
title       : Exploring mtcars
subtitle    : Slidify presentation for Developing Data Products
author      : Cutberto Paredes
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
ext_widgets : {rCharts: [libraries/nvd3]}
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = FALSE)
knitr::opts_chunk$set(message =  FALSE)
```
## Introduction

- This is a brief exploration of the mtcars dataset that comes with R.

- First, let's declare as factors those variables that are actually factors.

```{r Preprocess1}
mtcars$am <- factor(mtcars$am, labels = c('Automatic', 'Manual'))
mtcars$vs <- factor(mtcars$vs)
mtcars$gear <- factor(mtcars$gear)
mtcars$cyl <- factor(mtcars$cyl)
```

- Also, let's add a new field: $hp/mt$. This value was found by Henderson and 
Velleman (1981) to explain $mpg$. We'll do regression in a bit.

```{r Preprocess2}
mtcars$rhpwt <- mtcars$hp / mtcars$wt
```

---
## Pairs Plot

This plot shows the correlation between pairs of variables.

```{r ggpairs, echo = FALSE, fig.width=12, fig.align='center'}
library(ggplot2)
library(GGally)
ggpairs(mtcars, mapping = aes(bins = 25))
```

---
## Linear Regression Model

This command fits a linear regression model using $hp$, $rhpwt$ and $am$ as 
interacting regressors. Both $r^2$ and coefficients are shown below.

```{r fitLM}
fit <- lm(mpg ~ hp*rhpwt*am, mtcars)
```

```{r summary, echo=FALSE}
summary(fit)[c(8,4)]
```

---
## Interactive Plot

This rCharts plot shows the relationship between $mpg$ and $rhpwt$.

```{r plot, echo = FALSE, results = 'asis'}
library(rCharts)
library(knitr)
n1 <- rPlot(mpg ~ rhpwt, data = mtcars, color = 'am', type = 'point')
n1
```